Differential invariant signatures for planar Lie group transformations of images

### 2019-12-17 paper/newpaper.tex
Tidying up repository

Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
be written in coordinates as $(x_i, y_i)$. Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$. Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$. Then the Omega Process is a second-order differential operator defined by: 
\begin{equation}
\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} &
\frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} &
\frac{\partial}{\partial y_j} \end{vmatrix} = 
\frac{\partial^2}{\partial x_i
\partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
\end{equation}

Under the above affine transformation, $\Omega_{ij} \mapsto \det A^{-1} \Omega_{ij}$. Note that $\det A^{-1}$ has no dependence on the coordinates. 
The Omega Process can be applied to pairs of smooth functions as follows, writing $\frac{\partial f}{\partial x}$ as $f_x$:

\begin{equation}
\Omega_{ij} f(x_i, y_i) g(x_j, y_j) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
\end{equation}

Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$ that only vary by a scaling factor of $\det A^{-1}$ when $\mathbf{x}$ is mapped by an affine transformation. This matches the definition of a first-order partial transvectant of two functions:

@@

Under this formula we end with a factor $\det A^{-r}$ in place of $\det
A^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
\mathbf{b}$. $r$ is referred to as the weight of the partial
transvectant. It can also be useful to consider the maximum order of
derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.

@@

We consider as our image, the following function, defined on $[-1, 1]
\times:
[-1, 1]$
\begin{equation}\label{eq:function}
  \begin{split}
    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
  \end{split}
\end{equation}
This function was chosen to have no critical points, and to be
predominantly linear, so that the higher order derivatives were not too
large. This was predominantly so the higher order terms in the signatures
would not overwhelm the smaller terms. The function is depicted as a
greyscale image in Figure~\ref{fig:function}
\begin{figure}
  \centering
  \includegraphics[width=12cm]{figures/function}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function}.}\label{fig:function}
\end{figure}

We consider the signatures of this function under various transformation
groups, as detailed throughout the main body of the paper and illustrate
the signature in three dimensions. A grid is overlaid on the image of the
function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
mapped to the signature surface to help understand what the signature looks
like locally.
\begin{figure}
  \centering
  \includegraphics[width=12cm]{figures/function_scanlines}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function} with a grid of lines
overlaid.}\label{fig:function_scanlines}
\end{figure}

@@

\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4 are actually invariants.} Then we can write this bit. 
I3 is Robert's one.}
%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$. Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way. But I can't see how else to get $f_{ii}$!

>>>>

Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
be written in coordinates as $(x_i, y_i)$. Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$. Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + \mathbf{b}$ where $A \in GL(2,\mathbb{R}$) and $\mathbf{b} \in \mathbb{R}^2$. Then the Omega Process is a second-order differential operator defined by: 
\begin{equation}
\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} &
\frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} &
\frac{\partial}{\partial y_j} \end{vmatrix} = 
\frac{\partial^2}{\partial x_i
\partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
\end{equation}

Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
\Omega_{ij}$. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
The Omega Process can be applied to pairs of smooth functions as follows,
writing $\frac{\partial f}{\partial x}$ as $f_x$:

\begin{equation}
\Omega_{ij} \left(f(x_i, y_i) g(x_j, y_j)\right) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
\end{equation}

Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$
that only vary by a scaling factor of $(\det A)^{-1}$ when $\mathbf{x}$ is
mapped by an affine transformation. This matches the definition of a
first-order partial transvectant of two functions:

@@

Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
\mathbf{b}$. $r$ is referred to as the weight of the partial
transvectant. It can also be useful to consider the maximum order of
derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.

@@

We consider as our image, the following function, defined on $[-1, 1]
\times:
[-1, 1]$
\begin{equation}\label{eq:function}
  \begin{split}
    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
  \end{split}
\end{equation}
This function was chosen to have no critical points, and to be
predominantly linear, so that the higher order derivatives were not too
large. This was predominantly so the higher order terms in the signatures
would not overwhelm the smaller terms. The function is depicted as a
greyscale image in Figure~\ref{fig:function}
\begin{figure}
  \centering
  \includegraphics[width=12cm]{Figs/function}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function}.}\label{fig:function}
\end{figure}

We consider the signatures of this function under various transformation
groups, as detailed throughout the main body of the paper and illustrate
the signature in three dimensions. A grid is overlaid on the image of the
function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
mapped to the signature surface to help understand what the signature looks
like locally.
\begin{figure}
  \centering
  \includegraphics[width=12cm]{Figs/function_scanlines}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function} with a grid of lines
overlaid.}\label{fig:function_scanlines}
\end{figure}

@@

\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4
are actually invariants. Then we can write this bit. I3 is Robert's one.}
%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$. Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way. But I can't see how else to get $f_{ii}$!
